Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
network construction

<!-- TODO: better lead in -->
Within each layer, we generated proximity-based social networks using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We 
assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within the spatial distance 
threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. <!-- TODO: simplify here-->For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
<!-- eg this is connecting contexts used to calculate layer similarity -->

>>>>

We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
individuals were associating if simultaneous GPS fixes were within the spatial
distance threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the spatial distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal treshold of 5 minutes
and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].

<!--In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .-->
<!-- eg this is connecting contexts used to calculate layer similarity -->
